Data Flow Analysis\\in the Presence of Correlated Calls

### 2014-12-10 content/background.tex
remove obsolete comments

\subsection{IFDS}\label{sec:bgifds}
The IFDS framework~\cite{reps1995precise} is a precise and efficient algorithm for data-flow analysis
%. IFDS was developed in 1995 by T.\,Reps, S.\,Horwitz, and M.\,Sagiv at the University of Wisconsin and
that has been used to solve a variety of data-flow analysis problems~\cite{bodden2013spl,naeem2008typestate,DBLP:conf/birthday/KreikerRRSWY13,tripp2009taj}.
%\mtodo{ The four references take away space in the References section. Remove some of them?  }
The IFDS framework is an instance of the \textit{functional approach} to data-flow analysis~\cite{pnueli1981two}
because it constructs summaries of the effects of called procedures.
\commentout{The IFDS analysis is a version of the classic \textit{functional approach} to data-flow analysis proposed by M.\,Sharir and A.\,Pnueli~\cite{pnueli1981two}.}
\commentout{In other data-flow algorithms not based on the functional approach, the result of the analysis at the entry of a procedure ``merges'' the incoming data obtained from all callers of the procedure. As a consequence, there is one global data-flow result computed at the end of the procedure. Context-sensitivity, however, allows an analysis to compute the data-flow result for a given procedure as a \textit{function} of the data-flow value at the start of the procedure. 
In other words, the analysis result for a procedure varies depending on where the procedure was called from. This significantly improves the precision of a data-flow analysis, which is why context-sensitivity is an important advantage of IFDS over classic data-flow algorithms.}
\mtodo{I'm not saying any more that IFDS is a version of Sharir\&Pnueli's functional approach.}
\mtodo{I also removed the comparison of IFDS with other algorithms. I'm not pointing out the benefits of IFDS any more, so we might fail to show the importance of the algorithm.}
The IFDS framework is applicable to \textit{inter-procedural} data flow problems whose domain is \textit{subsets} of a \textit{finite} set $D$,
and whose data-flow functions are \textit{distributive}.
A function $f$ is distributive if 
$f(x_1\sqcap x_2)=f(x_1)\sqcap f(x_2)$.

@@

\mtodo{We never use the interpretation function, so I deleted it, too}
\commentout{
To convert a representation relation $R_f$ back into the original flow function $f$, we can use the \textit{interpretation} function $\denote {R_f}$:
\begin{align}
  f&=\denote{R_f}\notag\\
  &=\lambda D_1\,.\,\left(\left\{d_2\ |\ \exists d_1\in D_1:\,(d_1,\,d_2)\in R_f\right\}\cup\{d_2\ |\ (\mathbf0,\,d_2)\in R_f\}\right)
  \setminus\{\mathbf0\}\,.
\end{align}
}

>>>>

\subsection{IFDS}\label{sec:bgifds}
The IFDS framework~\cite{reps1995precise} is a precise and efficient algorithm for data-flow analysis
%. IFDS was developed in 1995 by T.\,Reps, S.\,Horwitz, and M.\,Sagiv at the University of Wisconsin and
that has been used to solve a variety of data-flow analysis problems~\cite{bodden2013spl,naeem2008typestate,DBLP:conf/birthday/KreikerRRSWY13,tripp2009taj}.
%\mtodo{ The four references take away space in the References section. Remove some of them?  }
The IFDS framework is an instance of the \textit{functional approach} to data-flow analysis~\cite{pnueli1981two}
because it constructs summaries of the effects of called procedures.
\commentout{The IFDS analysis is a version of the classic \textit{functional approach} to data-flow analysis proposed by M.\,Sharir and A.\,Pnueli~\cite{pnueli1981two}.}
\commentout{In other data-flow algorithms not based on the functional approach, the result of the analysis at the entry of a procedure ``merges'' the incoming data obtained from all callers of the procedure. As a consequence, there is one global data-flow result computed at the end of the procedure. Context-sensitivity, however, allows an analysis to compute the data-flow result for a given procedure as a \textit{function} of the data-flow value at the start of the procedure. 
In other words, the analysis result for a procedure varies depending on where the procedure was called from. This significantly improves the precision of a data-flow analysis, which is why context-sensitivity is an important advantage of IFDS over classic data-flow algorithms.}
The IFDS framework is applicable to \textit{inter-procedural} data flow problems whose domain is \textit{subsets} of a \textit{finite} set $D$,
and whose data-flow functions are \textit{distributive}.
A function $f$ is distributive if 
$f(x_1\sqcap x_2)=f(x_1)\sqcap f(x_2)$.

@@

\commentout{
To convert a representation relation $R_f$ back into the original flow function $f$, we can use the \textit{interpretation} function $\denote {R_f}$:
\begin{align}
  f&=\denote{R_f}\notag\\
  &=\lambda D_1\,.\,\left(\left\{d_2\ |\ \exists d_1\in D_1:\,(d_1,\,d_2)\in R_f\right\}\cup\{d_2\ |\ (\mathbf0,\,d_2)\in R_f\}\right)
  \setminus\{\mathbf0\}\,.
\end{align}
}
